Figures

### 2019-12-01 figures/07_model-selection.Rmd
dont add sd to re_global

```{r tp_re, fig.width=3.25, fig.height=4.5}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
fit_tp$re <- fit_tp$re %>%
  mutate_at(vars(matches("%")), function(x) x + 
              as.numeric(fit_tp$re_global["50%"]))

>>>>

```{r tp_re, fig.width=3.25, fig.height=4.5}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
# fit_tp$re <- fit_tp$re %>%
#   mutate_at(vars(matches("%")), function(x) x + 
#               as.numeric(fit_tp$re_global["50%"]))
